### 2018-08-30 README.Rmd
update github readme

[![Build Status](https://api.travis-ci.org/dynverse/dynbenchmark.svg)](https://travis-ci.org/dynverse/dynbenchmark)
![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg) <img src="package/man/figures/logo.png" align="right" />

@@

## Structure

This repository is structured as follows:

* data: raw data files required by the scripts
* derived: data files produced by the scripts
* figures: figures created by the scrips
* manuscript: source files for producing the manuscript
* package: an R package with helper functions
* results: data objects outputted by the scripts
* scripts: code required to reproduce the analyses of the benchmark

@@

```{r results = 'asis'}
knit_nest("scripts")
```

>>>>

[![Build Status](https://api.travis-ci.org/dynverse/dynbenchmark.svg)](https://travis-ci.org/dynverse/dynbenchmark)
![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg) <a href = "package/man/figures/logo.svg"><img src="package/man/figures/logo.png" align="right" /></a>

@@

## Experiments

From start to finish, the repository is divided into several experiments, each with their own scripts and results. The scripts and results are accompanied by documentation using github READMEs and can be easily explored by going to the appropriate folders:

```{r results = 'asis'}
extract_scripts_documentation("scripts", recursive = FALSE) %>% 
  mutate(
    scripts = location,
    results = map_chr(scripts, dynbenchmark::link_to_results)
  ) %>% 
  mutate(
    ix = case_when(is.na(ix) ~ "", TRUE ~ as.character(ix)),
    id = label_long(id),
    scripts = paste0("[", id, " scripts](", scripts, ")"),
    results = case_when(is.na(results) ~ "", TRUE ~ paste0("[", id, " results](", results, ")"))
  ) %>% 
  select(`\\#` = ix, id, scripts, results) %>% 
  knitr::kable()
```

We also have several additional subfolders:

* manuscript: source files for producing the manuscript
* package: an R package with several helper functions
* data: raw data files required by the scripts
* derived: intermediate data files produced by the scripts

@@
